Near and mid-infrared properties of known $z\geq5$ Quasars

### 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180530.tex
VHzQs figures big update

\title[Very high-$z$ Quasars]
        {Near and mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

\maketitle
\begin{abstract}
Very high redshift quasars are excellent probes of physics the early
Universe.  Understanding how billion solar mass black holes
formed, evolve and accrete in the first billion years is a key
outstanding problem in contemporary astrophysics, and one that wil lbe
directly addressed by upcoming missions such as ESA {\it Euclid} and
the {\it James Webb Space Telescope}.
%%
We can gain a good appreciation for what these missions will discover
by collating the datasets we currently have, and in this paper, we,
for the first time since the discovery of $z\geq5.00$ quasars assemble all spectroscopically confirmed very high redshift quasars in
one catalogue.
%%
In particular we present the near ($z/Z, y/Y, J, H, K_{s}$ and $K$)
infrared and mid-infrared (WISE) properties of all 424
spectroscopically known redshift $z\geq5$ quasars.  Using archival public
WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
in the near-infrared and find blah.  We present a comprehensive series
of colour-redshift and colour-colour plots and make inferences into
the hot dust properties of the very high-redshift quasar
population. Extrapolating the known quasar luminosity function we
suggest that 80\% of the possibly detected $z\geq5$ quasars in the
current datasets have been discovered.
\end{abstract}

@@

\iffalse
\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
\item Concentrate on NIR and W1/W2
\item SED dust plot with just W1/W2...
\item Check vs. Assef R90/C75 catalog.
\end{itemize}

\noindent
{\bf For NJGC: }
\begin{itemize}
\item Write the NIR data section(s) 
\end{itemize}

\noindent
{\bf For Both: }
\begin{itemize}
\item Need to decide what mags and mag system we are reporting, especially in the 
NIR...
\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
\end{itemize}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Q; and defined here to have redshifts
$z\geq5.00$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

Super-Eddington (also called super-critical) accretion is a viable
physical mechanism to explain the high luminosity and rapid growth of
supermassive black holes in the early universe
\citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
Volonteri2015, Pezzulli2016, Lupi2016} Thus, one might well expect
VH$z$Qs to vary in luminosity as they potentially go through phases of
Super-Eddington accretion and these should be looked for, especially
when the e.g.  near-infrared $K$-band is sampling rest-frame
$\approx$3670, 3145, 2750\AA\ at redshifts $z=5, 6$ and 7,
respectively.

The build-up of SMBHs via accretion is important due to the desire to
understand the evolution of the black hole mass function (BHMF) and
since there is a remarkable similarity between cosmic star-formation
rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
BHAR trace each other \citep[with a normalisation factor of
$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
at higher redshift, $z>4$. The physical reasons for this are currently very poorly
understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
stellar mass of the bulge and galaxy total stellar mass,
respectively. The evolution and potential importance of the SFRD and BHAR 
link is a key outstanding problem in contemporary astrophysics, 
potentially explaining the galaxy-black hole scaling relations. 
However, there may also simply be a non-causal origin of the black-hole 
galaxy scaling relations \citep{Jahnke2011}.

Quasars are also known to be prodigious emitters of infrared emission,
thought to be from the thermal emission of dust grains heated by
continuum emission from the accretion disc \citep[][]{Hill2014,
Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
allow discrimination between AGN\footnote{Historically, ``quasars'' and
``Active Galactic Nuclei (AGN)'' have described different
luminosity/classes of objects, but here we use these terms
interchangeably (with a preference for quasar) in recognition of the
fact that they both describe accreting supermassive black holes
\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
Timlin2016} as well as AGN and star-forming galaxies due to the
presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
\citep[e.g., ][]{Yan2007, Tielens2008}.

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, those authors demonstrate that the hot-dust
abundance in the 21 quasars builds up in tandem with the growth of the
central black hole.

WISE mapped the sky in 4 passbands, in bands centered at wavelengths
of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
``ALLWISE'' catalog, contains nearly 750 million detections at
high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
detections of 17 (55\%) of the then known 31 quasars at $z >
6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
data release, as opposed to the superior ``AllWISE'' catalogs. That
sample only examined the 31 known $z>6$ quasars; our sample has 148
objects with redshift $z \geq 6.00$.

Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
with Table 8 of][]{Banados2016}. Our motivations are numerous and
include: {\it (i)} establishing the first complete catalogue of
$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
reporting homogenous near-infrared photometry for the quasars; {\it
(iii)} making the first study of NIR variability of the VHzQ
population and {\it (iv)} establishing the photometric properties for
upcoming surveys and telescopes, e.g. the Large Synoptic Survey
Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
ESA {\it
Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
and the {\it James Webb Space Telescope}
(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}

We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
of garnishing a large sample, adequately spanning physical properties 
(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
we have gained over the last couple of decades since $z>5$ quasars were 
discovered.

@@

This paper is organized as follows.  In Section 2, we present the
assembled list of the 424 $z\leq5.00$ VH$z$Qs that we have
compiled. We then give a high-level overview of the photometric
surveys and datasets we use and present the photometry of the VH$z$Qs.
In Section 3 we In Section 4 we and we then note our Conclusions in
Section 5.

We make the somewhat unconventional decision to present all our
photometry and magnitudes on the AB zero-point system
\citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared,
as well as the mid-infrared magnitudes.  Because of established
conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point
system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
magnitudes are calibrated on the Vega system (Wright et al. 2010). For
WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339,
5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about
Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
Filter. We make use of the Explanatory Supplement to the WISE All-Sky
Data Release, as well as the WISE AllWISE Data Release Products
online.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km
s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} =
0.693$ (Planck Collaboration et al. 2016) in order to be consistent
with \citet{Banados2016}.

@@

\begin{figure*}
%%trim=l b r t
  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

We assemble our dataset in a relatively straightforwad manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

We then obtain optical, near-infrared and mid-infrared photometry for the
spectral dataset.

The optical data comes from the 
Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.

The near-infrared data comes from the Wide Field Camera (WFCAM) on 
the United Kingdom Infra-Red Telescope

@@

Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
and \citet{Matsuoka2018b}.

\input{THE_TABLE_v0pnt96_TOP10_betterformat}

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey   & \# VH$z$Qs & Notes  \\
\hline  
  ATLAS      &    4    &  \\
  CFHQS     &  20    &  \\
  DELS        &    2    &  \\
  ELAIS       &    1    &  \\
  FIRST       &    1    &  \\
  HSC         &    8    &  \\
  IMS          &   1     &  \\
  MMT        &  12    &  \\
  NDWFS    &  1      &  \\
  PSO          &    84  & \\
  RD           &  1       & \\
  SDSS        & 156       & \\
  SOUV       & 20       & \\
  SDWISE    & 27& \\
  SHELLQs  & 55 & \\
  ULAS       & 10& \\
  VDES       & 11& \\
  VIK          & 9 &\\
  VIMOS     & 1& \\
\hline  \hline
\end{tabular}
\caption{ATLAS \citet{Shanks2015}; }
      \label{tab:surveys}
\end{table}

@@

    We query and return the mean PSF magnitudes from the $grizy$ filters
    ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
    sample. Details of our SQL and links to the main tables are given
    in~\ref{sec:PS1_SQL}.

    \subsubsection{DECam}

@@

\section{NIR Data}

The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

In this paper we include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017 and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (200910..) to 1st April 2016, to get as much coverage as
possible. Hence, the NIR is extremely heterogeneous.

The data was processed using a forced photometry, or matched-aperture
photometry. A pipeline for this has been developed by WFAU, but
has not yet been incorporated into the main VDFS pipeline. Full details of the
matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
2018, in prep, and has also been discussed in \citet{Cross2013} and \citet{Cross2017}.
We will give the pertinent points of the MAP and specific details of these data sets below.

\subsection{Selection of NIR}

The first step of the process was to ingest the catalogue of VHzQs into
the WSA/VSA. These data are in the table \verb+finalQsoCatalogue+. Next we set
up new programmes WSERV1000, VSERV1000 in the WSA and VSA respectively. We
assign all frames that contain the high-z QSO based on WCS information in the
WSA to WSERV1000, but adding a new line to the table \verb+ProgrammeFrame+ and
same in VSA for VSERV1000. Assigning these frames to a separate programme allows
us to process them together and put them into a single release.

\subsection{Setup Matched Aperture Product}

Add a new entry \verb+RequiredMatchedApertureProduct+

\begin{itemize}
\item mapID	archiveName	programmeID	extractor	mapType	name	description	selection	finalProductTable	addSurveyList
\item 1	1	WSA	10999	CASU	2	highzQsoMap	Variability via matched apertures for set of high-z QSOs	SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue	highzQsoMapVariability	NONE
\end{itemize}

Explain

Entries in \verb+RequiredMapAverages+

Add table?
\begin{table*}
  \begin{center}
    \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lll lll lll l}
\hline \hline
                &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
\hline
      1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
      2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
      3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
      4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
      5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
      6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
      \hline \hline
      \label{tab:The_Numbers}
    \end{tabular}
    \caption{}
  \end{center}
\end{table*}

\subsection{Processing MAP data}

A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
but the layer is a general abstraction that allows multiple sources of
catalogue, and multiple types\ldots
Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent

\subsubsection{Forced photometry}
CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
the input list equal to objects selected to be within \ldots of the multiframe
centre. In this case, where there are 424 QSOs spread across the sky, there is
typically 1 object per multiframe, but many have two and one,
multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
is a multi-extension FITS binary table, with identical columns to the CASU FITS
binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
VISTA survey products and also familiar to many astronomers through the INTWFS
\citep{}, and VST-ATLAS and -VPHAS \citep{}. Since forced photometry can be run
in many ways on a particular image, a single science frame is not
necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
information on what processing stage they are at ({\bf bitProcessingFlag}),
whether they have been ingested ({\bf isIngested}), or what quality control has
been run on them ({\bf ppErrBitsStatus}).

>>>>

\title[Very high-$z$ Quasars]
        {Near and mid-infrared properties of known $z\geq5$ Quasars}
\author[N.P. Ross et al.]
       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk} and Nicholas J. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

\maketitle
\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.
%%
Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Qs, defined here to have redshifts
$z\gtrsim5$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.  However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.  For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}. 
%%However, we also note the potential for the non-causal origins of the
%%black-hole galaxy scaling relations \citep{Jahnke2011}.

Quasars are also known to be prodigious emitters of infrared emission,
thought to be from the thermal emission of dust grains heated by
continuum emission from the accretion disc \citep[][]{Hill2014,
Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
allow discrimation between AGN\footnote{Historically, ``quasars'' and
``Active Galactic Nuclei (AGN)'' have described different
luminosity/classes of objects, but here we use these terms
interchangeably (with a preference for quasar) in recognition of the
fact that they both describe accreting supermassive black holes
\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
Timlin2016} as well as AGN and star-forming galaxies due to the
presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
\citep[e.g., ][]{Yan2007, Tielens2008}.

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, we demonstrate that the hot-dust abundance in
the 21 quasars builds up in tandem with the growth of the central
black hole,

\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
(55\%) of the then known 31 quasars at $z > 6$. However,
\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
as opposed to the superior ``AllWISE'' catalogs. That sample only
examined the 31 known $z>6$ quasars; our sample has 148 objects with
redshift $z\geq6.00$.

Here we update \citet{Jiang2010}  and \citet{Blain2013} 
\citep[along with Table 8 of][]{Banados2016}.

We chose redshift $z=5.0$ as our lower redshift limit due to a combination 
of garnishing a large sample, adequately spanning physical properties 
(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
we've gained over the last couple of decades since $z>5$ quasars were 
discovered.

WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013}, \citet{Stern2012}

In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission. This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).  The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys. %%

\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter,

@@

$M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass, stellar mass of the bulge and 
 galaxy total stellar mass, respectively.

Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}. We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online. All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in order to be consistent with \citet{Banados2016}.

@@

\input{THE_TABLE_v0pnt96_TOP10}

@@

%% From Banado2016
%% Fan et al. (2000) [2000AJ....120.1167F];     3 = Fan et al. (2001) [2001AJ....122.2833F];     4 = Fan et al. (2003) [2003AJ....125.1649F];     5 = Fan et al. (2004) [2004AJ....128..515F];     6 = Mahabal et al. (2005) [2005ApJ...634L...9M];     7 = Cool et al. (2006) [2006AJ....132..823C];     8 = Fan et al. (2006a) [2006AJ....131.1203F];     9 = Goto et al. (2006) [2006MNRAS.371..769G];    10 = Mcgreer et al. (2006) [2006ApJ...652..157M];    11 = Carilli et al. (2007) [2007ApJ...666L...9C];   12 = Kurk et al. (2007) [2007ApJ...669...32K];    13 = Stern et al. (2007) [2007ApJ...663..677S];    14 = Venemans et al. (2007a) [2007MNRAS.376...76V];    15 = Willott et al. (2007) [2007AJ....134.2435W];    16 = Jiang et al. (2008) [2008AJ....135.1057J];    17 = Wang et al. (2008b) [2008ApJ...687..848W];    18 = Jiang et al. (2009) [2009AJ....138..305J];    19 = Kurk et al. (2009) [2009ApJ...702..833K];    20 = Mortlock et al. (2009) [2009A&A...505...97M];    21 = Willott et al. (2009) [2009AJ....137.3541W];    22 = Carilli et al. (2010) [2010ApJ...714..834C];   23 = Wang et al. (2010) [2010ApJ...714..699W];    24 = Willott et al. (2010a) [2010AJ....140..546W];    25 = Willott et al. (2010b) [2010AJ....139..906W];    26 = Derosa et al. (2011) [2011ApJ...739...56D];    27 = Mortlock et al. (2011) [2011Natur..474..616M];   28 = Wang et al. (2011) [2011ApJ...739L..34W];   29 = Zeimann et al. (2011) [2011ApJ...736...57Z];    30 = Morganson et al. (2012) [2012AJ....143..142M];    31 = Venemans et al. (2012) [2012ApJ...751L..25V];   32 = Mcgreer et al. (2013) [2013ApJ...768..105M];    33 = Venemans et al. (2013) [2013ApJ...779...24V];   34 = Wang et al. (2013) [2013ApJ...773...44W];   35 = Willott et al. (2013b) [2013ApJ...770...13W];    36 = Banados et al. (2014) [2014AJ....148...14B];    37 = Calura et al. (2014) [2014MNRAS.438.2765C];    38 = Leipski et al. (2014) [2014ApJ...785..154L];   39 = Banados et al. (2015a) [2015ApJ...805L...8B];   40 = Banados et al. (2015b) [2015ApJ...804..118B];   41 = Becker et al. (2015) [2015PASA...32...45B];    42 = Carnall et al. (2015) [2015MNRAS.451...16C];    43 = Jiang et al. (2015) [2015AJ....149..188J];    44 = Kashikawa et al. (2015) [2015ApJ...798...28K];   45 = Kim et al. (2015) [2015ApJ...813L..35K];   46 = Reed et al. (2015) [2015MNRAS.454.3952R];    47 = Venemans et al. (2015a) [2015MNRAS.453.2259V];    48 = Venemans et al. (2015b) [2015ApJ...801L..11V];   49 = Willott et al. (2015) [2015ApJ...801..123W];   50 = Wu et al. (2015) [2015Natur..518..512W];    51 = Venemans et al. (2016) [2016ApJ...816...37V];   52 = Wang-Feige et al. (2016) [labaApJ...819...24W];   53 = Matsuoka et al. (2016) [2016arXiv160302281M];   54 = Wang et al. (2016) [2016arXiv160609634W];
Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a}
and \citet{Matsuoka2018b}.

@@

We query and return the mean PSF magnitudes from the $grizy$ filters
({\tt MeanPSFMag}) which are in the AB system for our 425 VH$z$Q
sample. Details of our SQL and links to the main tables are given
in~\ref{sec:PS1_SQL}.

@@
